Cleaning Tropical Andes plant GBIF occurrence records

### 2023-08-02 code/L1/L1_TropicalAndes_plants_GBIF.Rmd
update tests, remove plot, and update record removal

```{r}
flags <- clean_coordinates(x = TropicalAndes_GBIF_plant_occ,
                           lon = "decimalLongitude",
                           lat = "decimalLatitude",
                           countries = "countryCode",
                           species = "species",
                           tests = c("capitals", "centroids", "countries",
                                     "duplicates", "equal", "gbif",
                                     "institutions", "seas","zeros"))
summary(flags)
plot(flags, lon = "decimalLongitude", lat = "decimalLatitude")
```

```{r}
#exclude problematic records
TropicalAndes_GBIF_plant_occ_cleaned <- TropicalAndes_GBIF_plant_occ[flags$summary,]
TropicalAndes_GBIF_plant_occ_flagged <- TropicalAndes_GBIF_plant_occ[!flags$summary,]
```

>>>>

```{r}
flags <- clean_coordinates(x = TropicalAndes_GBIF_plant_occ,
                           lon = "decimalLongitude",
                           lat = "decimalLatitude",
                           countries = "countryCode",
                           species = "species",
                           tests = c("capitals", "centroids",
                                     "duplicates", "equal", "gbif",
                                     "institutions", "seas","zeros"))
summary(flags)
```

```{r}
#exclude problematic records
TropicalAndes_GBIF_plant_occ_cleaned <- TropicalAndes_GBIF_plant_occ[flags$.summary,]
TropicalAndes_GBIF_plant_occ_flagged <- TropicalAndes_GBIF_plant_occ[!flags$.summary,]
```
